---
title: "R Notebook"
output: html_notebook
---

**This script is to Test Google impacts on the country level**

```{r}
rm(list=ls())
library(geosphere)
library(dplyr)
```


# Read Google impacts

```{r}
# Alternative 1: read the data from pre-saved file
HiGoogleTrend <- read.csv("./Data/Google/india.csv",header=FALSE)
KoGoogleTrend <- read.csv("./Data/Google/southkorea.csv",header=FALSE)
RuGoogleTrend <- read.csv("./Data/Google/russia.csv",header=FALSE)
JaGoogleTrend <- read.csv("./Data/Google/japan.csv",header=FALSE)
DeGoogleTrend <- read.csv("./Data/Google/germany.csv",header=FALSE)
ItGoogleTrend <- read.csv("./Data/Google/italy.csv",header=FALSE)

# CHOOSE TIME DURATION IN 01.22-04.20
GoogleTrends_chosen_date = c(2:91) 

HiGoogleImpact = HiGoogleTrend[GoogleTrends_chosen_date,]
KoGoogleImpact = KoGoogleTrend[GoogleTrends_chosen_date,]
RuGoogleImpact = RuGoogleTrend[GoogleTrends_chosen_date,]
JaGoogleImpact = JaGoogleTrend[GoogleTrends_chosen_date,]
DeGoogleImpact = DeGoogleTrend[GoogleTrends_chosen_date,]
ItGoogleImpact = ItGoogleTrend[GoogleTrends_chosen_date,]
```


# Read immediacy data 

```{r}
countryLoc <- read.csv("./Data/countries_locations.csv")
countryLoc$name = as.character(countryLoc$name)
targetNameLoc = c("India","South Korea","Russia","Japan","Germany","Italy")
targetLoc <- countryLoc[countryLoc$name %in% targetNameLoc,]
sourceLoc <- countryLoc[!(countryLoc$name %in% targetLoc$name),]

geo_dist = c()
for (i in 1:nrow(targetLoc)){
  target_dist = c()
  long = targetLoc[i,]$longitude
  lat = targetLoc[i,]$latitude
  target_loc = c(long,lat)
  
  for (i in 1:nrow(countryLoc)){
    long = countryLoc[i,]$longitude
    lat = countryLoc[i,]$latitude
    source_loc = c(long,lat) 
    target_dist <- append(target_dist,distm(target_loc,source_loc,fun=distHaversine))
  }
  
  geo_dist <- append(geo_dist,target_dist)
}

geo_dist_matrix <- matrix(geo_dist, ncol=nrow(countryLoc), byrow=TRUE)
geo_dist <- as.data.frame(geo_dist_matrix, stringsAsFactors=FALSE)

rownames(geo_dist) = targetLoc$name
colnames(geo_dist) = countryLoc$name
```


# Process feature data

```{r}
# Deal with confirm data
confirm <- read.csv("./Data/0423covid19_confirmed.csv")
allColNames = colnames(confirm)
remColNames = c("Province.State","Country.Region","Lat","Long")
chosenCol <- allColNames[!allColNames %in% remColNames]

# Summarise confirmed cases by country
confirm %>%
  group_by(Country.Region) %>%
    summarise_at(chosenCol,sum) -> confirmByCountry
confirmByCountry$Country.Region = as.character(confirmByCountry$Country.Region)

# Repeat for death data
death <- read.csv("./Data/0423covid19_deaths.csv")
allColNames = colnames(death)
remColNames = c("Province.State","Country.Region","Lat","Long")
chosenCol <- allColNames[!allColNames %in% remColNames]

# Summarise death cases by country
death %>%
  group_by(Country.Region) %>%
    summarise_at(chosenCol,sum) -> deathByCountry
deathByCountry$Country.Region = as.character(deathByCountry$Country.Region)

```


# Test the relevance btw immediacy and Google impact

**FIRST: Calculate the correlation btw source feature and target impact**
**Switch between Confirm and DeathR manully in thie section**

```{r}
target_nodes = c("Hi","Ko","Ru","Ja","De","It")
feat_chosen_dates = c(2:91)

flag = targetNameLoc %in% confirmByCountry$Country.Region # By testing, we found South Korea is named differently in confirm datasets by 'Korea, South'

cor = c()
pval = c()
sourceNames = c()

for (i in 1:length(target_nodes)){
  dname = paste(target_nodes[i],"GoogleImpact",sep="")
  impact = get(dname)
  
  for (j in 1:nrow(countryLoc)){
    countryName = countryLoc[j,]$name
    if(countryName=="South Korea") {countryName="Korea, South"}
    
    if (countryName %in% confirmByCountry$Country.Region) {
      sourceNames = append(sourceNames,countryName)
      confirmSource = confirmByCountry[confirmByCountry$Country.Region==countryName,feat_chosen_dates]
      
      ## Switch BEGIN
      
      ### For Confirm Feature
      # sourceFeat = as.numeric(confirmSource[1,])
      # sumry = cor.test(sourceFeat,impact[,2])
      # targetcor = sumry$estimate
      # pvalue = sumry$p.value
      # cor = append(cor,targetcor)
      # pval = append(pval,pvalue)

      ### For DearthR Feature
      deathSource = deathByCountry[deathByCountry$Country.Region==countryName,feat_chosen_dates]
      deathRSource = deathSource/confirmSource
      deathRSource[is.na(deathRSource)] = 0
      sourceFeat =  as.numeric(deathRSource[1,])
      if(sd(deathRSource)!=0){
        sumry = cor.test(sourceFeat,impact[,2])
        targetcor = sumry$estimate
        pvalue = sumry$p.value
      
       cor = append(cor,targetcor)
        pval = append(pval,pvalue)
      }
      else{
        cor = append(cor,0)
        pval = append(pval,0)
      }
    
      ## Switch END
      
    }
  }
}

sourceNames[sourceNames=="Korea, South"] = "South Korea"

cor_matrix <- matrix(cor, ncol=length(cor)/length(target_nodes), byrow=TRUE)
correlation <- as.data.frame(cor_matrix, stringsAsFactors=FALSE)
colnames(correlation) = sourceNames[1:ncol(correlation)]
rownames(correlation) = target_nodes

pval_matrix <- matrix(pval, ncol=length(cor)/length(target_nodes), byrow=TRUE)
pvalue <- as.data.frame(pval_matrix, stringsAsFactors=FALSE)
colnames(pvalue) = sourceNames[1:ncol(correlation)]
rownames(pvalue) = target_nodes
  
```


**Second step: calculate correlation btw disatnce and above correlations**

```{r}
geo_dist = geo_dist[,colnames(correlation)]
targetNameLoc = c("India","South Korea","Russia","Japan","Germany","Italy")
targetNameLocId = c("Hi","Ko","Ru","Ja","De","It")

corCorDist = c()
pvalCorDist = c()

for (i in 1:length(targetNameLoc)){
  
  chosentargetId = i
  
  corTarget = as.data.frame(t(correlation[targetNameLocId[chosentargetId],]))
  geodistTarget = as.data.frame(t(geo_dist[targetNameLoc[chosentargetId],]))
  geoRowNames = rownames(geodistTarget)
  
  sumry = cor.test(geodistTarget[,1],corTarget[,1])
  corCorDist = append(corCorDist,sumry$estimate)
  pvalCorDist = append(pvalCorDist,sumry$p.value)
}

corCorDistt_matrix <- matrix(corCorDist, ncol=6, byrow=TRUE)
corCorDist <- as.data.frame(corCorDistt_matrix, stringsAsFactors=FALSE)
colnames(corCorDist) = targetNameLocId

pvalCorDist_matrix <- matrix(pvalCorDist, ncol=6, byrow=TRUE)
pvalCorDist <- as.data.frame(pvalCorDist_matrix, stringsAsFactors=FALSE)
colnames(pvalCorDist) = targetNameLocId

print(corCorDist)
print(pvalCorDist)

```


# Further exploration

**Plot the distance interval wrt coorelation from the first step**

```{r}
# png("./pic/DeathRGoogleCorDist/It_GoogleCorDist.png",height=350,width=700)

targetNameLoc = c("India","South Korea","Russia","Japan","Germany","Italy")
targetNameLocId = c("Hi","Ko","Ru","Ja","De","It")
chosentargetId = 5

corTarget = as.data.frame(t(correlation[targetNameLocId[chosentargetId],]))
geodistTarget = as.data.frame(t(geo_dist[targetNameLoc[chosentargetId],]))

title = paste(targetNameLoc[chosentargetId],"'s Correlation wrt Sources at Chosen Geo-distance Threshold",sep="")
plot(geodistTarget[,1],corTarget[,1],main=title,ylim=c(0,1),ylab="Correlation",xlab="Distance (m)",col="gray73")

# dev.off()
```


