---
title: "R Notebook"
author: "Haojun Cai"
date: "17/4/2020"
output: html_notebook
---

**This script is to Test Twitter impacts on the region level**

```{r}
rm(list=ls())
```


# Calculate distance matrix of geolocation

```{r}
calGeoDistMatrix <- function(source_nodes,target_nodes,node_geo){
  geo_dist = c()
  
  for (i in 1:length(target_nodes)){
    target = target_nodes[i]
    target_dist = c()
    lat = node_geo[node_geo$Node==target,]$lat
    long = node_geo[node_geo$Node==target,]$long
    target_loc = c(long,lat)
    
    for (source in source_nodes){
      lat = node_geo[node_geo$Node==source,]$lat
      long = node_geo[node_geo$Node==source,]$long
      source_loc = c(long,lat) 
      target_dist <- append(target_dist,distm(target_loc,source_loc,fun=distHaversine))
    }
    
   geo_dist <- append(geo_dist,target_dist)
  }
  
  geo_dist_matrix <- matrix(geo_dist, ncol=length(source_nodes), byrow=TRUE)
  geo_dist <- as.data.frame(geo_dist_matrix, stringsAsFactors=FALSE)
  
  colnames(geo_dist) = source_nodes
  rownames(geo_dist) = target_nodes

  return(geo_dist)
}
```


# Test the relevance btw immediacy and Twitter impact

## FIRST: Calculate the correlation btw source feature and target impact

```{r}
calFeatTwitter <- function(test_targets,test_sources,TwitterImpact){
  cor = c()
  pval = c()
  for (target in test_targets){
    target = tolower(target)
    
    for (source in test_sources){
      dname = paste(source,"_weight",sep="")
      source_weight = get(dname)

      sumry = cor.test(source_weight,TwitterImpact[,target])
      pvalue = sumry$p.value
      targetcor= sumry$estimate
      
      cor = append(cor,targetcor)
      pval = append(pval,pvalue)
      # plot(source_weight, TwitterImpact$de, xlab="Features", ylab="Impacts")
    }
  }
  
  cor_matrix <- matrix(cor, ncol=length(test_sources), byrow=TRUE)
  correlation <- as.data.frame(cor_matrix, stringsAsFactors=FALSE)
  colnames(correlation) = test_sources
  rownames(correlation) = test_targets
  
  pval_matrix <- matrix(pval, ncol=length(test_sources), byrow=TRUE)
  pvalue <- as.data.frame(pval_matrix, stringsAsFactors=FALSE)
  colnames(pvalue) = test_sources
  rownames(pvalue) = test_targets
  
  return(list("cor"=correlation,"pval"=pvalue))
}
```


## FIRST: Calculate coorelation between distance and above source-target-coorelations

**Alternative 1: Geographical distance**

```{r}
calcorCorGeodist <- function(test_targets,correlation,geo_dist){
  
  TargetDistCor = c()
  pval = c()
  
  for (target in test_targets){
    targetcor = correlation[c(target),]
    targetdist = sort(geo_dist[c(target),])
    sortcolnames <- colnames(targetdist)
    targetcor <- targetcor[,sortcolnames] # Sort the coorelation based on descending distance
    targetcor <- t(targetcor)
    targetdist <- t(targetdist)
  
    sumry = cor.test(targetcor,targetdist)
    pvalue = sumry$p.value
    cor= sumry$estimate
    
    TargetDistCor = append(TargetDistCor,cor)
    pval = append(pval,pvalue)
  }
  
  TargetDistCor_matrix <- matrix(TargetDistCor, ncol=length(target_nodes), byrow=TRUE)
  TargetDistCor <- as.data.frame(TargetDistCor_matrix, stringsAsFactors=FALSE)
  colnames(TargetDistCor) = target_nodes
  
  pval_matrix <- matrix(pval, ncol=length(target_nodes), byrow=TRUE)
  pvalue <- as.data.frame(pval_matrix, stringsAsFactors=FALSE)
  colnames(pvalue) = target_nodes
  
  return(list("cor"=TargetDistCor,"pval"=pvalue))
  
}  
```


**Alternative 2: Shorteset path**

```{r}
calcorCorPath <- function(test_targets,correlation,short_paths){

  pathDist <- short_paths[,c(source_nodes)]
  rownames(pathDist) = short_paths[,c("X")]
  pathDist = pathDist[c(target_nodes),]
  
  geo_dist = pathDist
  TargetDistCor = c()
  pval = c()
  
  for (target in test_targets){
    targetcor = correlation[c(target),]
    targetdist = sort(geo_dist[c(target),])
    sortcolnames <- colnames(targetdist)
    targetcor <- targetcor[,sortcolnames] # Sort the coorelation based on descending distance
    targetcor <- t(targetcor)
    targetdist <- t(targetdist)

    sumry = cor.test(targetcor,targetdist)
    pvalue = sumry$p.value
    cor= sumry$estimate
    
    TargetDistCor = append(TargetDistCor,cor)
    pval = append(pval,pvalue)
  }

  TargetDistCor_matrix <- matrix(TargetDistCor, ncol=length(target_nodes), byrow=TRUE)
  TargetDistCor <- as.data.frame(TargetDistCor_matrix, stringsAsFactors=FALSE)
  colnames(TargetDistCor) = target_nodes
  
  pval_matrix <- matrix(pval, ncol=length(target_nodes), byrow=TRUE)
  pvalue <- as.data.frame(pval_matrix, stringsAsFactors=FALSE)
  colnames(pvalue) = target_nodes
  
  return(list("cor"=TargetDistCor,"pval"=pvalue))
}

```


# Deal with data within 02.09 - 04.20 (features, impacts)

# Define sources and targets

```{r}
source_nodes = c("Eu1","Eu2","Eu3","Eu4","Eu5","Eu6","Eu7","Au","As1","As2","As3","As4","As5","Am1","Am2","Am3","Af1","Af2")
target_nodes = c("Hi","Ko","Ru","Ja","De","It")
```


# Read Twitter impacts

```{r}
TwitterImpact <- read.csv("./Data/0421TweetsStatistics.csv")
TwitterImpact <- TwitterImpact[1:72,] # CHOOSE TIME DURATION IN 02.09-04.20
```


# Read immediacy data
```{r}
short_paths <- read.csv("./Data/Nodes/shortest_path.csv")
node_geo <- read.csv("./Data/Nodes/node_geo.csv")
member <- read.csv("./Data/Nodes/node_member.csv")
geo_dist <- calGeoDistMatrix(source_nodes,target_nodes,node_geo)
```


# Read source features

```{r}
# Change test_srouce and test_targets to test different variables
test_targets = target_nodes
test_sources = source_nodes

# Read source features
feat_chosen_dates = c(19:90) # CHOOSE TIME DURATION IN 02.09 - 04.20

# Read source features
for (source in test_sources){
  varname = paste(source,"_source_feat",sep="")
  source_feat = read.csv(paste("./Data/Nodes/features/",source,".csv",sep=""))
  source_feat = source_feat[feat_chosen_dates,] 
  assign(varname,source_feat)
}
```


# Calculate coorelation between chosen source feature/source weight and impacts

TEST 1: Confirm, Twitter impacts
**First step: calculate correlation btw source feature and target impacts**

```{r}
# Calculate weighted source features
for (source in test_sources){
  dname = paste(source,"_source_feat",sep="")
  varname = paste(source,"_weight",sep="")
  source_feat = get(dname)
  source_weight = source_feat$confirm
  assign(varname,source_weight)
}

sumryFeatTwitter <- calFeatTwitter(test_targets,test_sources,TwitterImpact)
corFeatTwitter <- sumryFeatTwitter$cor
pvalFeatTwitter <- sumryFeatTwitter$pval
print(corFeatTwitter)
print(pvalFeatTwitter)

```


TEST 1 Continued: Confirm, Twitter impacts, Distance
**Second step: calculate correlation btw disatnce and above correlations**

```{r}
sumryCorGeodist <- calcorCorGeodist(test_targets,corFeatTwitter,geo_dist)
corCorGeodist <- sumryCorGeodist$cor
pvalCorGeodist <- sumryCorGeodist$pval
print(corCorGeodist)
print(pvalCorGeodist)

sumryCorPath <- calcorCorPath(test_targets,corFeatTwitter,short_paths)
corCorPath <- sumryCorPath$cor
pvalCorPath <- sumryCorPath$pval
print(corCorPath)
print(pvalCorPath)
```


TEST 2: **DeathR**, Twitter impacts
**First step: calculate correlation btw source feature and target impacts**

```{r}
# Calculate weighted source features
for (source in test_sources){
  dname = paste(source,"_source_feat",sep="")
  varname = paste(source,"_weight",sep="")
  source_feat = get(dname)
  source_weight = source_feat$DeathR
  assign(varname,source_weight)
}

sumryFeatTwitter <- calFeatTwitter(test_targets,test_sources,TwitterImpact)
corFeatTwitter <- sumryFeatTwitter$cor
pvalFeatTwitter <- sumryFeatTwitter$pval
print(corFeatTwitter)
print(pvalFeatTwitter)
```


TEST 2 continuted: **DeathR**, Twitter impacts, Distance
**Second step: calculate correlation btw disatnce and above correlations**

```{r}
sumryCorGeodist <- calcorCorGeodist(test_targets,corFeatTwitter,geo_dist)
corCorGeodist <- sumryCorGeodist$cor
pvalCorGeodist <- sumryCorGeodist$pval
print(corCorGeodist)
print(pvalCorGeodist)

sumryCorPath <- calcorCorPath(test_targets,corFeatTwitter,short_paths)
corCorPath <- sumryCorPath$cor
pvalCorPath <- sumryCorPath$pval
print(corCorPath)
print(pvalCorPath)
```





